---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `kueh` R Color Palettes

[_Kueh_(粿)](https://en.wikipedia.org/wiki/Kuih) are Southeast Asian pastries as varied and variegated as they are delicious. Hoping to whet the hunger of your audience with your R plots in that next presentation? Look no further!

The setup of this package was inspired by [`LaCroixColorR`](https://github.com/johannesbjork/LaCroixColoR) and [`ghibli`](https://github.com/ewenme/ghibli).

```{r salat_cars}
library(kueh)

with(mtcars, {
  cyl = factor(cyl)
  n = length(levels(cyl))
  plot(disp, drat, col = kueh_palette('lapis_sagu', n)[cyl], pch = 19L)
})
```

The following palettes are available:

```{r all_palettes}
all_palettes = kueh_palettes()
all_palettes
```

Which look like:

```{r plot_palettes}
par(mfrow = n2mfrow(length(all_palettes)))
for (ii in seq_along(all_palettes)) print(kueh_palette(names(all_palettes)[ii]))
```

Three types of color palette are available -- `discrete` (default), `continuous` (via `colorRampPalette`), and `paired` (the `discrete` colors, but darkened & lightened):

```{r palette_types}
par(mfrow = c(1L, 3L))
print(kueh_palette('ang_ku', type = 'discrete'))
print(kueh_palette('ang_ku', n = 500L, type = 'continuous'))
print(kueh_palette('ang_ku', type = 'paired'))
```


